---
title: "Extra_Tutorial_Practice"
output: html_document
date: "2024-10-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Exercise 1: Bar Chart with mpg Dataset
Objective: Create a bar chart to visualize the number of cars by manufacturer using the mpg dataset from the ggplot2 package.

1. Load the dataset: mpg from ggplot2.
2. Group by manufacturer and count the number of cars for each.
3. Plot a bar chart using Plotly:
  x-axis: Manufacturer
  y-axis: Count of cars
4. Customize the bar chart:
  Add color to represent different manufacturers.
  Use a title and axis labels for clarity.

```{r}
#enter code
```

##Exercise 2: Scatter Plot with mtcars Dataset
Objective: Create a scatter plot to show the relationship between horsepower and miles per gallon using the mtcars dataset.

1.Load the dataset: mtcars from base R.
2. Plot a scatter plot using Plotly:
  x-axis: Horsepower (hp)
  y-axis: Miles per gallon (mpg)
  Size: Set the size of points based on the number of cylinders (cyl).
  Color: Use colors to represent different cylinder counts.
4. Customize the scatter plot:
  Add a title and labels for both axes.   
  Adjust the size and color scale for better visualization.
  
```{r}
#enter code
```
  
##Exercise 3: Line Chart with economics Dataset
Objective: Create a line chart to analyze the trend of unemployment over time using the economics dataset from the ggplot2 package.

1. Load the dataset: economics from ggplot2.
2. Plot a line chart using Plotly:
  x-axis: Date (date)
  y-axis: Unemployment (unemploy)
3. Customize the line chart:
  Add a title and labels for the x and y axes.
  Adjust the line color and width.
4. Optionally, add a hover template to show the date and unemployment rate more clearly.

```{r}
#enter code
```

