---
title: "Extra_Tutorial_Practice_Solutions"
output: html_document
date: "2024-10-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Exercise 1: Bar Chart with mpg Dataset
Objective: Create a bar chart to visualize the number of cars by manufacturer using the mpg dataset from the ggplot2 package.

1. Load the dataset: mpg from ggplot2.
2. Group by manufacturer and count the number of cars for each.
3. Plot a bar chart using Plotly:
  x-axis: Manufacturer
  y-axis: Count of cars
4. Customize the bar chart:
  Add color to represent different manufacturers.
  Use a title and axis labels for clarity.

```{r}
#enter code
# Load necessary libraries
library(plotly)
library(ggplot2)

# Load the dataset
data("mpg")

# Summarize data by manufacturer
mpg_summary <- mpg %>%
  dplyr::count(manufacturer)

# Create bar chart
plot_ly(
  data = mpg_summary,
  x = ~manufacturer,
  y = ~n,
  type = 'bar',
  marker = list(color = ~manufacturer)
) %>%
  layout(
    title = "Number of Cars by Manufacturer",
    xaxis = list(title = "Manufacturer"),
    yaxis = list(title = "Count")
  )
```

##Exercise 2: Scatter Plot with mtcars Dataset
Objective: Create a scatter plot to show the relationship between horsepower and miles per gallon using the mtcars dataset.

1.Load the dataset: mtcars from base R.
2. Plot a scatter plot using Plotly:
  x-axis: Horsepower (hp)
  y-axis: Miles per gallon (mpg)
  Size: Set the size of points based on the number of cylinders (cyl).
  Color: Use colors to represent different cylinder counts.
4. Customize the scatter plot:
  Add a title and labels for both axes.   
  Adjust the size and color scale for better visualization.
  
```{r}
#enter code
# Load necessary libraries
library(plotly)

# Load the dataset
data("mtcars")

# Create scatter plot
plot_ly(
  data = mtcars,
  x = ~hp,
  y = ~mpg,
  type = 'scatter',
  mode = 'markers',
  marker = list(size = ~cyl * 2, color = ~cyl, colorscale = "Viridis")
) %>%
  layout(
    title = "Horsepower vs. Miles Per Gallon",
    xaxis = list(title = "Horsepower"),
    yaxis = list(title = "Miles per Gallon")
  )
```
  
##Exercise 3: Line Chart with economics Dataset
Objective: Create a line chart to analyze the trend of unemployment over time using the economics dataset from the ggplot2 package.

1. Load the dataset: economics from ggplot2.
2. Plot a line chart using Plotly:
  x-axis: Date (date)
  y-axis: Unemployment (unemploy)
3. Customize the line chart:
  Add a title and labels for the x and y axes.
  Adjust the line color and width.
4. Optionally, add a hover template to show the date and unemployment rate more clearly.

```{r}
#enter code
# Load necessary libraries
library(plotly)
library(ggplot2)

# Load the dataset
data("economics")

# Create line chart
plot_ly(
  data = economics,
  x = ~date,
  y = ~unemploy,
  type = 'scatter',
  mode = 'lines',
  line = list(color = 'blue')
) %>%
  layout(
    title = "Unemployment Over Time",
    xaxis = list(title = "Date"),
    yaxis = list(title = "Unemployment")
  )
```

